---
title: "Tyler1"
output: html_document
---

Simmulate a social network 
1a for i in 1,…,n respondents simulate a position in a 2-dimensional space 
using a draw from a 2d normal distribution
```{r}
rm(list = ls())
setwd('/Users/yuezhou/Desktop/TYLER')
n <- 100
x <- rnorm(n, mean = 0, sd = 1)
y <- rnorm(n, mean= 0, sd = 1)
plot(x, y)
```
#1b compute the n*n matrix of Euclidean distances between individuals 
```{r}
A <- cbind(x, y)
distance <- dist(A)
distance <- as.matrix(distance)
```
For each pair of individuals (say individual i and individual j), 
simulate an edge using a draw from a bernoulli distribution with a success probability 
equal to exp(a*d_ij)/(1+exp(a*d_ij)) where d_ij is the distance between i and j computed in 1b 
and a is a constant that controls the overall expected tie frequency. 
```{r}
a = 0.1
probability <- exp(a * distance)/ (1+exp(a*distance))
rvariable <- rbinom(n*n, 1, as.vector(probability))
rvariable = matrix(rvariable, ncol = n, nrow = n)
plot(x, y)
for(i in 1:n){
  for(j in 1:n){
    if (rvariable[i, j] == 1){
    segments(x[i],y[i],x[j],y[j])
    }
  }
}
```
Simulate covariates for each individual in the network 
2a simulate each individual’s age and gender 
by taking a draw from a distribution that looks like the us population age distribution 
and flipping a fair coin, respectively. 
```{r}
age <- runif(n, min = 0, max =100)
gender <- rbinom(n, 1, 1/2)
```
2b Now simulate an outcome for each person. 
Take a draw from a standard normal with mean equal to beta0+beta1*gender+beta2*age.
```{r}
beta0 <- 10
beta1 <- 10
beta2 <- 10
dontknow <- rnorm(n, mean = beta0 + beta1*gender + beta2*age, sd = 1)
```
Take a sample and compute a confidence interval
3a Randomly choosing a set of individuals 
then running a regression model to estimate beta1 and beta2. 
```{r}
index <-1:length(dontknow)
m <- 50 
somesample <- sample(index, m, replace=FALSE, prob = NULL)
dontknow[somesample]

reg <- lm(dontknow[somesample] ~ age[somesample] + gender[somesample])
reg
summary(reg)
```
Check if the confidence interval contains the true values of beta1 and beta2.
```{r}
confint(reg, "(Intercept)")
confint(reg, "age[somesample]")
confint(reg, "gender[somesample]")
```
Yes the confidence interval contains the true value of beta1 and beta 2

3b Now randomly sample *edges* from the social network
and evaluate in the same way as 3b.  
After doing this multiple times compute the coverage of the confidence intervals
```{r}
trials <- 100
countbeta1 <- 0
countbeta2 <- 0
index <-1:length(dontknow)
m <- 50 
for(i in 1:trials){
  somesample <- sample(index, m, replace=FALSE, prob = NULL)
  reg <- lm(dontknow[somesample] ~ age[somesample] + gender[somesample])
  summary(reg)
  interval1 = confint(reg, "age[somesample]")
  interval2 = confint(reg, "gender[somesample]")
  if (beta1 < interval1[2] && beta1 > interval1[1]) {
    countbeta1 <- countbeta1 + 1
  }
  if (beta2 < interval2[2] && beta2 > interval2[1]) {
    countbeta2 <- countbeta2 + 1
  }
}
countbeta1
countbeta2
```
After computing a hundred times, 
the fraction of times the true parameter beta1
is contained in the estimated interval is around 99/100
and the fraction of times the true parameter beta2
is contained in the estimated interval is around 60/100
```
