---
title: "Directional"
output: html_document
---

Simmulate a social network

```{r}
rm(list = ls())
setwd('/Users/yuezhou/Desktop/TYLER')
library(car)
```

simulate a position in a two-dimentional space

```{r}
n <- 100
x <- rnorm(n, mean = 0, sd = 1)
y <- rnorm(n, mean= 0, sd = 1)
```

compute the n*n matrix of Euclidean distances between individuals 

```{r}
A <- cbind(x, y)
distance <- dist(A)
distance <- as.matrix(distance)
```

create symmetric matrixs A, B and C as constant that times distance to simulate benefit and cost

from a link 

```{r}
a_0 <- 10
b_0 <- 5
c_0 <- 5

a <- rnorm(n*n, mean = a_0, sd = 1)
A <- matrix(a, nrow = n)
for(i in 1:n){
  for(j in 1:n){
    A[j,i] <- A[i,j]
  }
}

b <- rnorm(n*n, mean = b_0, sd = 1)
B <- matrix(b, nrow = n)
for(i in 1:n){
  for(j in 1:n){
    B[j,i] <- B[i,j]
  }
}

c <- rnorm(n*n, mean = c_0, sd = 1)
C <- matrix(c, nrow = n)
for(i in 1:n){
  for(j in 1:n){
    C[j,i] <- C[i,j]
  }
}

B_1 <- A * distance
B_0 <- B * distance
cost <- C * distance
benefit <- B_1 - B_0 
relation <- benefit - cost
```

creat a matric L represent the relationship between pairs of individuals

0 means there is no relationship between individuals i and j

1 means there is a relationship beteen individuals i and j

```{r}
L <- matrix(nrow = n, ncol = n)
for(i in 1:n){
  for(j in 1:n){
    if(relation[i,j] > 0){
      L[i,j] <- 1
    }else{
      L[i,j] <- 0
    }
  }
}
```

simulate an outcome Y for each pair of individuals 

Directional relationship

a forloop that runs the simulation trials times and get different confidence interval

```{r}
beta0 <- 10
beta1 <- 2
beta2 <- 3
beta3 <- 4
beta4 <- 5
beta5 <- 6

trials <- 100

confidence_1 <- matrix(NA, nrow = trials, ncol = 4)
confidence_2 <- matrix(NA, nrow = trials, ncol = 4)
confidence_3 <- matrix(NA, nrow = trials, ncol = 4)
confidence_4 <- matrix(NA, nrow = trials, ncol = 4)
confidence_5 <- matrix(NA, nrow = trials, ncol = 4)
```

generate matrix age_1 that has n rows with each row repeats the same age

age_2 that has n columns with each column repeats the same age

generate matrix gender_1 that has n rows with each row repeats the same gender

gender_2 that has n columns with each column repeats the same gender

```{r eval=FALSE}
for(h in 1:trials){
  cat("\n+")
  age1 <- runif(n, min = 0, max =100)
  repage1 <- rep(age1, time = n)
  age_1 <- matrix(repage1, nrow = n)
  age_2 <- matrix(repage1, nrow = n, byrow = T)
  
  gender1 <- rbinom(n, 1, 1/2)
  repgender1 <- rep(gender1, time = n)
  gender_1 <- matrix(repgender1, nrow = n)
  gender_2 <- matrix(repgender1, nrow = n, byrow = T)
  
  #so that when generating the outcome 
  #the outcome with each pair of individual can have a corresponding age, gender and link
  fittedoutcome <- beta0 + beta1*gender_1 + beta2*gender_2 + beta3*age_1+ beta4*age_2 + beta5*L
  
  #construct X, the matrix of all regressors
  rep_gender2 <- rep(gender1, each = n)
  gender.2 <- matrix(rep_gender2, ncol = 1)
  
  rep_gender1 <- rep(gender1, time = n)
  gender.1 <- matrix(rep_gender1, ncol = 1)
  
  rep_age2 <- rep(age1, each = n)
  age.2 <- matrix(rep_age2, ncol = 1 )
  
  rep_age1 <- rep(age1, time = n)
  age.1 <- matrix(rep_age1, ncol = 1 )
  
  link_ij <- matrix(L, ncol = 1, byrow = T)
  
  X <- cbind(rep_gender1, rep_gender2, rep_age1, rep_age2, link_ij)
  
  # Directionalrelationship 
  #when dyadic relationship is directional
  #Y_ij = Y_ji 
  #construct the residuals 
  someoutcome1 <- rnorm(n*n, mean = fittedoutcome, sd = 20)
  trueoutcome1 <- matrix(someoutcome1, nrow = n)
  fitted_outcome <- matrix(fittedoutcome, ncol = 1, byrow = T)
  reg <- lm(someoutcome1 ~ gender.1 + gender.2 + age.1 + age.2 + link_ij)
  reg_1 <- matrix(fitted(reg), ncol = n)
  u1 <- trueoutcome1 - reg_1
  
  #convert all the true regressors value into a matrix
  #compareCoefs(reg)    
  # coef <- matrix(compareCoefs(reg))
  coef <- summary(reg)$coefficients[, 1:2]
    
  #transpose X
  X_prime <- t(X)
  #X*X' 
  Y <- solve(X_prime%*%X)
  
  #calculate the variance using the paper's method
  m_ijkl <- 0
  suminside <- 0 
  for (i in 1:n) {
    cat(".")
    for (j in 1:n) {
      for (k in unique(c(i,j))){
        for (l in 1:n){
          m_ijkl <- 1
          X_ij <- X[(i-1) * n + j, ]
          u_ij <- u1[i,j]
          u_kl <- u1[k,l]
          X_kl <- X[(k-1) * n+l, ]
          inside <- m_ijkl *u_ij * u_kl * X_ij  %*% t(X_kl)
          suminside <- inside + suminside
        }
      }
      for (l in unique(c(i,j))){
        for (k in 1:n){
          if (k != i && k != j){
          m_ijkl <- 1
          X_ij <- X[(i-1) * n + j, ]
          u_ij <- u1[i,j]
          u_kl <- u1[k,l]
          X_kl <- X[(k-1) * n+l, ]
          inside <- m_ijkl *u_ij * u_kl * X_ij  %*% t(X_kl)
          suminside <- inside + suminside
          }
        }
      }
    }
  }
  suminside1 <- as.numeric(suminside)
  
  #compute variace of beta hat using method in the paper
  var <- Y %*% suminside %*% Y
  var[var < 0] <- 0
  
  #compute the confidence interval using the method in the paper
  conf_gender1l <- coef[2,1] - 1.96 * var[1,1]^0.5
  conf_gender1u <- coef[2,1] + 1.96 * var[1,1]^0.5
  c(conf_gender1l, conf_gender1u)
  
  conf_gender2l <- coef[3,1] - 1.96 * var[2,2]^0.5
  conf_gender2u <- coef[3,1] + 1.96 * var[2,2]^0.5
  c(conf_gender2l, conf_gender2u)
  
  conf_age1l <- coef[4,1] - 1.96 * var[3,3]^0.5
  conf_age1u <- coef[4,1] + 1.96 * var[3,3]^0.5
  c(conf_age1l, conf_age1u)
  
  conf_age2l <- coef[5,1] - 1.96 * var[4,4]^0.5
  conf_age2u <- coef[5,1] + 1.96 * var[4,4]^0.5
  c(conf_age2l, conf_age2u)
  
  conf_linkl <- coef[6,1] - 1.96 * var[5,5]^0.5
  conf_linku <- coef[6,1] + 1.96 * var[5,5]^0.5
  c(conf_linkl, conf_linku)
  
  #compute variace of beta hat using confint
  a_0 <- confint(reg, "(Intercept)")
  a0 <- matrix(a_0)
  
  a_1 <-confint(reg, "gender.1")
  a1 <- matrix(a_1)
  
  a_2 <-confint(reg, "gender.2")
  a2 <- matrix(a_2)
  
  a_3 <- confint(reg, "age.1")
  a3 <- matrix(a_3)
  
  a_4 <- confint(reg, "age.2")
  a4 <- matrix(a_4)
  
  a_5 <-confint(reg, "link_ij")
  a5 <- matrix(a_5)
  
  a_a <- cbind(a0, a1, a2, a3, a4, a5)
  
  #construct a matrix that contain all the confidence interval generated for beta1
  confidence_1[h,1] <- conf_gender1l
  confidence_1[h,2] <- conf_gender1u
  confidence_1[h,3] <- a1[1,1]
  confidence_1[h,4] <- a1[2,1]
  
  #construct a matrix that contain all the confidence interval generated for beta2
  confidence_2[h,1] <- conf_gender2l
  confidence_2[h,2] <- conf_gender2u
  confidence_2[h,3] <- a2[1,1]
  confidence_2[h,4] <- a2[2,1]
  
  #construct a matrix that contain all the confidence interval generated for beta3
  confidence_3[h,1] <- conf_age1l
  confidence_3[h,2] <- conf_age1u
  confidence_3[h,3] <- a3[1,1]
  confidence_3[h,4] <- a3[2,1]
  
  #construct a matrix that contain all the confidence interval generated for beta4
  confidence_4[h,1] <- conf_age2l
  confidence_4[h,2] <- conf_age2u
  confidence_4[h,3] <- a4[1,1]
  confidence_4[h,4] <- a4[2,1]
  
  #construct a matrix that contain all the confidence interval generated for beta5
  confidence_5[h,1] <- conf_linkl
  confidence_5[h,2] <- conf_linku
  confidence_5[h,3] <- a5[1,1]
  confidence_5[h,4] <- a5[2,1]
}

save.image("~/Desktop/TYLER/DIRECTIONAL RELATION.RData")

```

confidence intervals shown in graphs

```{r eval=FALSE}
#This is the function that draws the plot for confidence intervals
plotint <- function(confidence, beta, x.lab, dis1, dis2, dis3) {
  countbeta <- 0 
  countbeta.r <- 0 
  dim <- dim(confidence)[1]

  plot(NA, xlim = c(beta - dis1, beta + dis2 + dis3),
       ylim = c(0, dim), xlab = x.lab, ylab = "trials")
  abline(v = beta, col = "red")
  abline(v = beta + dis2, col = "red")
  n_1 <- 0
  for(h in 1:dim){
    segments(x0 = confidence[h,1], y0 = n_1, x1 = confidence[h,2], y1 = n_1)
    segments(x0 = confidence[h,3] + dis2, y0 = n_1, x1 = confidence[h,4] + dis2, y1 = n_1)
    midpoint_a <- (confidence[h,2] + confidence[h,1]) / 2
    points(midpoint_a, n_1)
    midpoint_r <- (confidence[h,3] + confidence[h,4] + 2 * dis2) / 2
    points(midpoint_r, n_1)
    if (beta < confidence[h,2] && beta > confidence[h,1]) {
      countbeta <- countbeta + 1
    }
    if (beta < confidence[h,4] && beta > confidence[h,3]) {
      countbeta.r <- countbeta.r + 1
    }
    n_1 <- n_1 + 1
  }
  return(c(countbeta, countbeta.r))
}

plotint(confidence_1, beta1, "adjusted beta1 vs regular beta1", 2, 3, 2)
plotint(confidence_2, beta2, "adjusted beta2 vs regular beta2", 2, 3, 2)
plotint(confidence_3, beta3, "adjusted beta3 vs regular beta3", 0.03, 0.05, 0.03)
plotint(confidence_4, beta4, "adjusted beta4 vs regular beta4", 0.03, 0.05, 0.03)
plotint(confidence_5, beta5, "adjusted beta5 vs regular beta5", 2, 3, 2)

save.image("Directional relationship")
```